% Created 2017-09-05 ter 08:21
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.2.1 (Org mode 9.0.9)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\textbf{Global Markets.} European equities are mixed while S\&P future is
falling 0.24\%. The Mexican peso is up 0.3\% against the USD and the
yield of the 10 years treasury is down to 2.13\%. Commodities: Oil is
up 1.4\% to USD48.00, steel is flat and soy is climbing 0.9\%.

\textbf{Local News}. Politics rules the day. In a much unexpected twist, the
Attorney General brought to light the information that his former
right arm may have helped Mr. Joesley Baptista in his plea bargain,
thus shedding a cloud of doubts over the whole affair.

Newspapers all around agree the whole thing should favor
Mr. Temer. For one, there are now doubts whether the second charge
against the President is going to go ahead at all. Secondly, the whole
affair against Mr. Temer looks so surreal by now that it may lose all
credibility and just unravel.

Be all that as it may, although still small, it follows that the odds
of a social security reform are now higher than they were a day ago,
and the market should price that in accordingly.  In a nutshell,
as natural consequence, Temer's political capital is likely to increase
while Congress' bargain power, shrink. Granted, it is certainly early
for a full assessment, but this is one of the main conclusions one can
gather out of this whole episode.

Economics also make a few headlines. Yet again, the O valor
underscores that analysts are more confident over economic
recovery. In the meantime, with the COPOM's decision due to tomorrow,
the debate of how long the Central Bank will go on cutting rates is
gaining some traction, as underscore by a couple of articles also at
the O Valor newspaper. In sum, the economy is also bring some positive
vibes for today's session.

\textbf{Agenda - Highlights}: \uline{Brazil}: Industrial Production of July - our
call: 0.8\%mom. US: durable goods order, July.

\rowcolors{2}{grey!15}{white}
\vspace{-0.5cm}
\begin{center}
\begin{tabular}{rlllll}
\textbf{Time} & \textbf{Country} & \textbf{Indicator} & \textbf{Period} & \textbf{Forecast} & \textbf{Impact}\\
\hline
09:00:00 & BZ & IP & July & 0,8\% mom & High\\
11:00:00 & US & Durable Orders & July & -3,3\% mom & Medium\\
\end{tabular}
\end{center}

\textbf{Bottom Line}. Local markets are likely celebrate the political
headlines.
\end{document}
